\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{center}
    \textbf{\Huge \scshape Daniel Truong} \\ \vspace{1pt}
    \href{https://linkedin.com/in/dantruong52435}{\underline{linkedin.com/in/dantruong52435}} $|$
    \href{https://github.com/dantruong}{\underline{github.com/dantruong}}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
  	\resumeSubHeadingListStart
    		\resumeSubheading
      		{State University of New York (SUNY) Polytechnic Institute}{Utica, NY}
      		{Master of Science in Information Design and Technology}{Jan. 2015 -- May  2021}
    		\resumeSubheading
      		{State University of New York at Oswego}{Oswego, NY}
      		{Bachelor of Science in Applied Mathematical Economics, Minor in Information Science}{Aug. 2009 -- May 2014}
  	\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  	\resumeSubHeadingListStart
    	\resumeSubheading
      		{State University of New York at Oswego}{Oswego, NY}
      		{Campus Technology Services}{Aug. 2011 - Present}
      		\resumeItemListStart
				\resumeItem{Programmer/Analyst (Jun. 2022 - Present)}
				{Design, develop and modify application programs on the college's administrative systems. Write programming code to meet user needs and specifications. Debug routine problems in application programs, prepare test data, and implement test changes. Advise individual users in identifying and solving technical problems.}
				\resumeItem{Technology Support Professional (Jun. 2018 - Jun. 2022)}
				{Provide instructional technology support for the School of Business and internal computing infrastructure. Imaging, configuring and installing physical computers in labs, advanced technology classrooms and faculty/staff offices, installing/upgrading campus and specialized software,  troubleshooting and facilitating hardware repairs, and administering campus desktop support applications.}
				\resumeItem{Desktop Support Technician (May 2014 - Jun. 2018)}
				{Provide "in-office" based technical support of hardware and software to the faculty, staff and departmental offices of SUNY Oswego. Installation and movement of campus computers, printers and peripheral equipment. Assisted with the creation and maintenance of O/S images, applying appropriate computer images to PC (and Macintosh) computers, and transferring client data when computers are replaced.}
				\resumeItem{Help Desk Assistant (Aug. 2011 - May 2014)}
				{Resolve computer software issues over the phone, via e-mail and in person, assisted in facilitation of new networking devices.}
      		\resumeItemListEnd
  	\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
  	\resumeSubHeadingListStart
    	\resumeSubItem{Evaluating Cloud-Based Gaming Solutions (May 2021)}{Overview on the performance of cloud-based gaming services such as Google Stadia, Nvidia GeForce Now and Xbox Cloud Gaming.}
	\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  	\resumeSubHeadingListStart
   		\resumeSubItem{NYS-Influenza-Map}{Data Visualization of Influenza cases in New York State using R and Shiny.}
    	\resumeSubItem{Coronavirus-Tracker-Map}{Data Visualization of COVID-19 cases in the US using R and Shiny.}
   		\resumeSubItem{jDungeonCrawler}{Dungeon-crawling text adventure game written in Java.}
    	\resumeSubItem{The High Screen}{Sports and Entertainment blog, powered by Jekyll.}
  	\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Programming Skills}
  	\resumeSubHeadingListStart
    	\resumeSubItem{Languages}{Java, Python, SQL (MySQL, PL/SQL), JavaScript, HTML/CSS, R, PHP} 
   		\resumeSubItem{Developer Tools}{R Studio, Jupyter, LaTeX, GitHub, Postman, VS Code, Netbeans, VMWare Fusion/Workstation}
    	\resumeSubItem{Web Frameworks}{Bootstrap,  Jekyll, Wordpress} 
  	\resumeSubHeadingListEnd

%-----------ADDITIONAL SKILLS-----------
\section{Additional Skills}
  	\resumeSubHeadingListStart
    	\resumeSubItem{Desktop Support}{Microsoft Endpoint Configuration Manager (MECM, formerly SCCM), Ivanti Endpoint Management, BeyondTrust Remote Support, ServiceNow}
   		\resumeSubItem{System Administration}{Windows Server 2012r2/2016/2019/2022, Active Directory, Hyper-V}
  	\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}